---
title: "fantasy"
output: pdf_document
---

# Overview

An analysis of a player.

```{r codeSetup, include=FALSE}
# Load libraries ----
# libraries required should already be loaded
library("rvest")
library("stringr")
library("tidyr")
library("TTR")
library (knitr)

```


# Data collection

Data for the player retreived for two seasons.

#2016-2017

Player's data from last season.
```{r, echo=FALSE}
KP16 <- read_html("http://www.euroleague.net/competition/players/showplayer?pcode=001255&seasoncode=E2016")
statsKP16<-KP16 %>%
    html_nodes("#tblPlayerPhaseStatistics .PlayerRankingContainer")%>%
    html_text() 
    
statsKP16<-as.numeric(statsKP16)
statsKP16


```

#2017-2018

Player's data from current season.
```{r, echo=FALSE}
KP17 <- read_html("http://www.euroleague.net/competition/players/showplayer?pcode=001255&seasoncode=E2017")
statsKP17<-KP17 %>%
    html_nodes("#tblPlayerPhaseStatistics .PlayerRankingContainer")%>%
    html_text() 
    
statsKP17<-as.numeric(statsKP17)
statsKP17


```


#Population
Data for all players.

```{r, echo=FALSE}
pir<- read_html("http://www.euroleague.net/main/statistics?mode=Leaders&entity=Players&seasonmode=Single&seasoncode=E2017&cat=Valuation&agg=Accumulated")
allpir<-pir %>%
    html_nodes("#main .game-center-statistics .StatsRowAlternatingGridResults td:nth-child(6)")%>%
    html_text() 

allpir<-as.numeric(allpir)
head(allpir)

```



#Statistics 2016-2017

Some basic statistics for the sample.


```{r, echo=FALSE}

summary(statsKP16)
shapiro.test(statsKP16)
```

#Statistics 2017-2018
Some basic statistics for the sample.


```{r, echo=FALSE}

summary(statsKP17)
shapiro.test(statsKP17)
```

Statistics of the population.

```{r, echo=FALSE}

summary(allpir)
shapiro.test(allpir)
```


# Plots

Histogram of player.

```{r, echo=FALSE}
hist(statsKP17,col="grey")
points(mean(statsKP17))
abline(v=mean(statsKP17))
```

A boxplot.

```{r, echo=FALSE}
boxplot(statsKP17)
points(mean(statsKP17))
abline(h=mean(statsKP17))
```

A normal q-q plot.

```{r, echo=FALSE}
qqnorm(statsKP17)
qqline(statsKP17)

```

Histogram of population.

```{r, echo=FALSE}
hist(allpir,col="grey")
points(mean(allpir))
abline(v=mean(allpir))
```

A boxplot.

```{r, echo=FALSE}
boxplot(allpir)
points(mean(allpir))
abline(h=mean(allpir))
```

A normal q-q plot.

```{r, echo=FALSE}
qqnorm(allpir)
qqline(allpir)

```
#Comparison

The probability of scoring 20 points is presented. A score is presented as well when the player belongs to the last 10% of all players.

```{r, echo=FALSE}
mu<-mean(allpir)
sdev<-sd(allpir)
percentile<-pnorm(20,mean=mu,sd=sdev,lower.tail = FALSE)
percentile

score<-qnorm(0.90,mu,sdev)
score

```

